---
title: "p2-ggmap"
author: "Yingbin Jiang"
date: "9/28/2017"
output: html_document
---
```{r, message=FALSE}
library(ggmap)
library(ggplot2)
library(leaflet)
library(htmltools)
library(dplyr)
library(plyr)
library(httr)
library(reshape2)
library(purrr)
library(rjson)
library(jsonlite)
library(geosphere)
library(gepaf)
library(geosphere)
library(stringr)

```


#Set input information 
```{r}
#Input Variables
in_mile = 0.2 
from = 'Chinatown, New York'
to = 'Bedford Av Station, Brooklyn'
route_dfa = route(from, to, structure = 'route', mode = 'transit',output = "all")
```

#Obtain transit location information and general nearby restaurant information 
```{r, warning=FALSE, message=FALSE}
latlon=decodePolyline(enc_polyline =route_dfa$routes[[1]]$overview_polyline$points)
steps = length(route_dfa$routes[[1]]$legs[[1]]$steps)
route_df = data.frame(matrix(nrow = (steps+1))) # define a new matrix and this matrix will replace route_df

# adding instruction, lats, lngs, address, content to each step
for (i in 1:steps){
  route_df$lat[i] = route_dfa$route[[1]]$legs[[1]]$steps[[i]]$start_location$lat
  route_df$lon[i] = route_dfa$route[[1]]$legs[[1]]$steps[[i]]$start_location$lng
  route_df$address[i] = revgeocode(c(as.numeric(route_df$lon[i]),as.numeric(route_df$lat[i])))
  route_df$url[i]=paste0("https://www.yelp.com/search?find_desc=Food&l=a:", route_df$lat[i],",", route_df$lon[i],",", "45")
  route_df$content[i] = paste("<b><a href=","'",route_df$url[i],"'>",route_df$address[i],"</a></b>","<br>")
  route_df$instruction[i] = route_dfa$route[[1]]$legs[[1]]$steps[[i]]$html_instructions
}

# the end location is different than others
route_df$lat[steps+1] = route_dfa$route[[1]]$legs[[1]]$steps[[steps]]$end_location$lat
route_df$lon[steps+1] = route_dfa$route[[1]]$legs[[1]]$steps[[i]]$end_location$lng
route_df$address[steps+1] = revgeocode(c(as.numeric(route_df$lon[steps]),as.numeric(route_df$lat[steps])))
route_df$url[steps+1]=paste0("https://www.yelp.com/search?find_desc=Food&l=a:", route_df$lat[steps+1],",", route_df$lon[steps+1],",", "45")
route_df$content[steps+1] = paste("<b><a href=","'",route_df$url[steps],"'>",route_df$address[steps],"</a></b>","<br>")
route_df$instruction[steps+1] = "Reach Destination"

trainsteps = c()
j = 1
for (i in 1:steps){
  if (!is.null(route_dfa$routes[[1]]$legs[[1]]$steps[[i]]$transit_details)){
    if(route_dfa$routes[[1]]$legs[[1]]$steps[[i]]$transit_details$line$vehicle$name == 'Subway'){
    trainsteps <- c(trainsteps, i)
    j = j+1
    }
  }
}

for (i in trainsteps){
  route_df$instruction[i] <- paste(route_dfa$routes[[1]]$legs[[1]]$steps[[i]]$transit_details$line$short_name, route_df$instruction[i] )
}
```

# Loading Data
```{r}
stop_times <- read.csv("../data/stop_times.txt")
stops <- read.csv("../data/stops.txt")
```

#Obtain train stop information
```{r}
stopdf = join(stop_times[,c(1,3,4,5)], stops[,c(1,3,5,6)], by='stop_id')

stopdf = subset(stopdf, (!is.na(stopdf$departure_time)))
stopdf['line'] = str_extract(stopdf$trip_id, "([A-Z0-9]{1})(?=\\.)")
stopdf$serviceday = str_extract(stopdf$trip_id, "[A-Z]{3}")
stopdf['direction'] <- str_sub(stopdf$stop_id, -1, -1)

stopdf <- stopdf[,c(-1)]

stopfinder <- function(trainline){

day <- weekdays(Sys.Date())

if (day == "Sunday"){
   day <- "SUN"
} else if (day == "Saturday"){
   day <- "SAT"
} else{
   day <- "WKD"
}

dfsubset = stopdf[(stopdf$line== trainline$line$short_name & stopdf$serviceday == day),]

trip <- c()

j <- 0
for (i in 1:dim(dfsubset)[1]){
  if (dfsubset$stop_sequence[i] == 1){
    j <- j + 1
  }
  trip <- c(trip, j)
}

dfsubset['trip'] <- trip
dfsubset['diff'] <- as.numeric(difftime(strptime(trainline$departure_time$text, format = "%H:%M"), as.POSIXct(paste(Sys.Date(), dfsubset$departure_time), format = "%Y-%m-%d %H:%M:%S")), units = "mins")

arrival_stop_name <- dfsubset$stop_name[which.min(distm(c(trainline$arrival_stop$location$lng, trainline$arrival_stop$location$lat), cbind(dfsubset$stop_lon, dfsubset$stop_lat)))]

departure_stop_name <- dfsubset$stop_name[which.min(distm(c(trainline$departure_stop$location$lng, trainline$departure_stop$location$lat), cbind(dfsubset$stop_lon, dfsubset$stop_lat)))]

nextN = dfsubset[(dfsubset$diff < 0 & dfsubset$stop_name == departure_stop_name & dfsubset$direction == "N"),][which.max(dfsubset[(dfsubset$diff < 0 & dfsubset$stop_name == departure_stop_name & dfsubset$direction == "N"),]$diff),]$trip
nextS = dfsubset[(dfsubset$diff < 0 & dfsubset$stop_name == departure_stop_name & dfsubset$direction == "S"),][which.max(dfsubset[(dfsubset$diff < 0 & dfsubset$stop_name == departure_stop_name & dfsubset$direction == "S"),]$diff),]$trip

if (dfsubset[dfsubset$trip == nextN & dfsubset$stop_name == arrival_stop_name,]$stop_sequence > dfsubset[dfsubset$trip == nextN & dfsubset$stop_name == departure_stop_name,]$stop_sequence){
  dfsubset <- dfsubset[dfsubset$trip == nextN,]
}else{
  dfsubset <- dfsubset[dfsubset$trip == nextS,]
}

dfsubset <- dfsubset[which(dfsubset$stop_name == departure_stop_name):which(dfsubset$stop_name == arrival_stop_name),]
return(dfsubset)
}

subway_res <- data.frame(matrix(ncol = 11, nrow = 0))
colnames(subway_res) <- c("departure_time", "stop_id", "stop_sequence", "stop_name", "stop_lat", "stop_lon", "line", "serviceday", "direction", "trip", "diff")
for (i in 1:length(trainsteps)){
  trainline <- route_dfa$routes[[1]]$legs[[1]]$steps[[trainsteps[i]]]$transit_details
  

  subway_res = rbind(subway_res, stopfinder(trainline))

}

subway_df <- data.frame(matrix(ncol = 7, nrow = nrow(subway_res)))
names(subway_df) <- names(route_df)

for (i in 1:nrow(subway_res)){
  subway_df$lat[i] = subway_res$stop_lat[i]
  subway_df$lon[i] = subway_res$stop_lon[i]
  subway_df$address[i] = paste(subway_res$stop_name[i])
  subway_df$url[i]=paste0("https://www.yelp.com/search?find_desc=Food&l=a:", subway_df$lat[i],",", subway_df$lon[i],",", "45")
  subway_df$content[i] = paste("<b><a href=","'",subway_df$url[i],"'>",subway_df$address[i],"</a></b>","<br>")
  subway_df$instruction[i] = paste("Subway on", subway_res$line[i], "line, in", subway_res$direction[i], "direction.")
}
```

#merging route_df and subway-df
```{r}

#accomodates at most 1 subway switch... for now
subway_begin <- 1
subway_end <- which(subway_res$line[-1] != subway_res$line[-length(subway_res$line)])
if(length(subway_end) == 0){subway_end <- nrow(subway_df)}

fin_df <- data.frame(matrix(ncol = 7, nrow = 0))
names(fin_df) <- names(route_df)

for (i in 1:nrow(route_df)){
  fin_df <- rbind(fin_df, route_df[i,])
  if (grepl("Subway towards",route_df$instruction[i])){
    fin_df <- rbind(fin_df, subway_df[subway_begin:subway_end,])
    subway_begin <- subway_end + 1
    subway_end <- nrow(subway_df)
  } 
}

route_df <- fin_df

route_df <- route_df[!is.na(route_df$address),]
```

#Obtain detailed restaurant information
```{r yelp search api}
res = POST("https://api.yelp.com/oauth2/token",
            body = list(grant_type = "client_credentials",
            client_id = "PN60TBfs2Dim2NyaDtFJcQ",
            client_secret = "gg5V6LvkqMcpuVWNMgnzpEajbedo3yxzWi4VeEZE2y7Pt7hqtzJsCts9srUpupf6"))
token = content(res)$access_token
yelp = "https://api.yelp.com"

 # create an empty ctb dataframe
ctb = data.frame(matrix(NA, nrow = 0, ncol = 14))

# a for loop for 4 locations in this case 
for (i in 1:nrow(route_df)){
  url_i =modify_url(yelp, path = c("v3", "businesses", "search"),
               query = list(latitude =route_df$lat[i],longitude = route_df$lon[i],
                            open_now = T,
                            radius =round(1609*in_mile,0)))
  res_i = GET(url_i, add_headers('Authorization' = paste("bearer", token)))
  #http_status(res)
  ctb_list_i = content(res_i)$businesses
  ctb_i=data.frame(matrix(NA, nrow = 0, ncol = 14))
  for (j in 1:length(ctb_list_i)){ # create a J row dataframe
    ctb_i[j,1] = ctb_list_i[[j]]$id
    ctb_i[j,2] = ctb_list_i[[j]]$name
    ctb_i[j,3] = ctb_list_i[[j]]$image_url
    ctb_i[j,4] = ctb_list_i[[j]]$url
    ctb_i[j,5] = ctb_list_i[[j]]$review_count
    ctb_i[j,6] = ctb_list_i[[j]]$rating
    ctb_i[j,7] = ifelse (is.null(ctb_list_i[[j]]$price),NA,ctb_list_i[[j]]$price)
    ctb_i[j,8] = ctb_list_i[[j]]$display_phone
    ctb_i[j,9] = ctb_list_i[[j]]$coordinates$latitude
    ctb_i[j,10] = ctb_list_i[[j]]$coordinates$longitude
    ctb_i[j,11] = ctb_list_i[[j]]$location$display_address[[1]]
    ctb_i[j,12] = ctb_list_i[[j]]$location$zip_code
    ctb_i[j,13] = ctb_list_i[[j]]$categories[[1]]$title
    ctb_i[j,14] = i 
  }
  ctb=rbind(ctb, ctb_i)
}

colnames(ctb) = c("id","name","image_url","url","review_count","rating","price","display_phone","latitude","longitude","address","zip code","category","stop")
ctb$price = factor(ctb$price)

```


#after searching on yelp will have the infor around the station and add more detials to rout_df dataframe
```{r add new yelp related column to route_df}
route_df=cbind(route_df,mean_stop =round(tapply(ctb$rating,ctb$stop,mean),2))# with 2 decimal places
```



```{r review and rate} 
for (i in 1:dim(ctb)[1]){
  url_rev_i = paste0("https://api.yelp.com/v3/businesses/",ctb$id[i],"/reviews")
  res_rev_i=GET(url_rev_i, add_headers('Authorization' = paste("bearer", token)))
  ctb$review_time[i] = content(res_rev_i)$review[[1]]$time_created # for review created time need to change
  ctb$review_rating[i] = content(res_rev_i)$review[[1]]$rating
  ctb$review_text[i] = content(res_rev_i)$review[[1]]$text
}
```


#Visualization # with stops hyperlink and average rating
```{r leaflet}
# the key part leaflet
factpal = colorFactor(rainbow(5), ctb$price)

leaflet(route_df) %>% addTiles() %>%
  addMarkers(route_df$lon, route_df$lat, popup = paste(route_df$content,"<br>",
                                                       "Overall Rating: ", "<b>",route_df$mean_stop,"</b>"))%>%
  addCircles(lng = ~lon, lat = ~lat, weight = 1,radius =1609*in_mile)%>%
  addPolylines(latlon$lon, latlon$lat,color="red")%>%
  addCircleMarkers(ctb$longitude, ctb$latitude, radius = ctb$rating+1, stroke = FALSE, # add 1 to make points bigger
                   fillOpacity = ((ctb$review_count - min(ctb$review_count)) / max(ctb$review_count - min(ctb$review_count)))+0.4,
                   color = factpal(ctb$price), 
                   popup = paste("<b><a href=", "'",ctb$url,"'>", ctb$name, "</a></b>","<br>",
                                 "Address: ",ctb$address ,"<br>",
                                 "Phone: ", "<a href=tel:", "'",ctb$display_phone,"'>", ctb$display_phone, "</a>","<br>",
                                 "Rating: ", ctb$rating, "<br>"
                               ))%>%
  addLegend(pal = factpal, values = ctb$price,
      title = "Price Range",
      opacity = 1
    )
```











